From Freebase to Wikidata: The Great Migration

### 2016-01-29 paper.tex
Reworked Section 1.

Large Web-based knowledge bases that make their data available
under free licenses in a~machine-readable form
have become central for the data strategy of many projects and organizations.
They find applications in areas as diverse as Web search,
natural language annotation, or translation.
Exemplary works are those of West \emph{et~al.}, who have proposed~\cite{west2014kb} a~way to
leverage existing Web search based question-answering technology to
fill in the gaps in knowledge bases in a~targeted way
or those of Gesmundo and Hall~\cite{gesmundo2014kb}, who have trained
a~syntactic parser paradigm that learns from large scale knowledge bases.

One such collaborative knowledge base is Freebase,
publicly launched by Metaweb in 2007 and acquired by Google in 2010.
Another example is Wikidata, a~collaborative knowledge base developed by
Wikimedia Deutschland since 2012 and operated by the Wikimedia Foundation.
Due to the success of Wikidata, Google announced in 2014 their intent to shut down Freebase and
help the community with the transfer of Freebase's content to Wikidata~\cite{freebase2014shutdown}.

@@

The paper is structured as follows.
First, we introduce Freebase and Wikidata in \autoref{sec:background}.
Then we describe our methodology and the metrics used to measure the migration
in \autoref{sec:challenges-of-the-migration}.
In order to support the migration, we have developed a~set of open source tools
that we present in \autoref{sec:primary-sources-tool}.
We then show the results of the migration
and discuss these statistics in \autoref{sec:statistics-of-the-migration}.
Before we close, we report on related work in \autoref{sec:related-work},
followed by an outlook at proposed next steps
and a~conclusion in \autoref{sec:future-work-and-conclusion}.

>>>>

Large Web-based knowledge bases that make their data available
under free licenses in a~machine-readable form
have become central for the data strategy of many projects and organizations.
They find applications in areas as diverse as Web search,
natural language annotation, or translation.
Exemplary works are those of West \emph{et~al.}, who in~\cite{west2014kb} have proposed a~way to
leverage Web search-based question answering technology to
fill in the gaps in knowledge bases in a~targeted way,
or research of Gesmundo and Hall~\cite{gesmundo2014kb}, who have trained
a~syntactic parser paradigm that learns from large-scale knowledge bases.

One such collaborative knowledge base is Freebase,
publicly launched by Metaweb in 2007 and acquired by Google in 2010.
Another example is Wikidata, a~collaborative know\-ledge base developed by
Wikimedia Deutschland since 2012 and operated by the Wikimedia Foundation.
Due to the success of Wikidata, Google announced in 2014 their intent to shut down Freebase and
help the community with the transfer of Freebase content to Wikidata~\cite{freebase2014shutdown}.

@@

The remainder of this paper is structured as follows.
First, we introduce Freebase and Wikidata in \autoref{sec:background}.
Then we describe our methodology and the metrics used to measure the migration
in \autoref{sec:challenges-of-the-migration}.
In order to support the migration, we have developed a~set of open source tools
that we present in \autoref{sec:primary-sources-tool}.
We then show the results of the migration
and discuss these statistics in \autoref{sec:statistics-of-the-migration}.
Before we close, we report on related work in \autoref{sec:related-work},
followed by an outlook at proposed next steps
and a~conclusion in \autoref{sec:future-work-and-conclusion}.
